Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
wording.

\subsection{Applying BDD to Haskell: An Example}
This section shows how behavior driven development works in practice,
by means of the Fibonacci function.  Of course this is a very simple
example, but the method is also applicable to more sophisticated
situations where design decisions might not be as obvious as here.

>>>>

\subsection{Applying BDD to Haskell: An Example}
This subsection shows how behavior driven development works in practice,
by means of the Fibonacci function.  Of course this is a very simple
example, but the method is also applicable to more sophisticated
situations where design decisions might not be as obvious as here.
